---
title: 
author: 
date: 
output: html_document
---

```{r setOptions, message=FALSE, echo=FALSE}
#script to generate mastr html report
#script should be called as R -e 'library(rmarkdown); library(stringr); 
#                                 mastrdir=getwd(); local_jsapi="/complgen2/mastr-procedure/displayChartHistogram.js" mastr <- str_replace(mastrdir,".*/([^/]*)","\\1");
#                                 knit2html("/complgen2/mastr-procedure/mastrreport.Rmd",
#                                             output=paste(mastr,"html",sep="."))'
library('ggplot2')
library('dplyr')
library('tidyr')
library('googleVis')
library('stringr')
library('DT')
op <- options(gvis.plot.tag='chart')

#aux function
google_jsapi_local <- function(googleChart, local_jsapi) {
  chartid <- googleChart$chartid
  script <- paste(readLines(local_jsapi, warn=F), collapse="\n")
  replacement <- paste('<script type="text/javascript">',
                      paste(script, chartid, "()", sep =""), "</script>", sep = '\n')
  googleChart$html$chart[c('jsChart')] <- replacement
  return(googleChart)  
}
```

```{r loaddata, results='asis', echo=FALSE}
setwd(mastrdir)
statsfile = paste(mastrdir, '/reports/report_stats-',mastr,'.tsv',sep='')
if (file.exists(statsfile)) {
	# create old demultiplex format used in rest of code (keep compatible if only demultiplex file is present)
	demultiplex <- read.delim(statsfile,sep='\t')
	demultiplex = demultiplex[demultiplex$parameter == 'fw_numreads',]
	demultiplex$SampleID = demultiplex$sample
	demultiplex$NumberOfClustersPF = as.integer(levels(demultiplex$value))[demultiplex$value]
	demultiplex = droplevels(demultiplex)
} else {
	demultiplexfile = paste(mastrdir, '/demultiplex_stats.tsv',sep='')
	demultiplex <- read.delim(demultiplexfile)
}
avg_cov <- read.delim(file=Sys.glob(paste(mastrdir,'/*coverage*avg*',sep=''))[1],sep='\t',header=T)
frac_cov_file <- Sys.glob(paste(mastrdir,'/*coverage*frac*',sep=''))[1]
frac_cov <- read.delim(file = frac_cov_file, sep='\t', header=T)

frac <- sub('.+_above_([0-9]+).tsv', '\\1', frac_cov_file, perl = T)

ampliconsfile = Sys.glob(paste(mastrdir,'/*.mastr/samplicons*.tsv', sep=''))[1]
if (!file.exists(ampliconsfile)) {
	ampliconsfile = Sys.glob(paste(mastrdir,'/samples/*/reg_*amplicons*.tsv', sep=''))[1]
}
amplicons  <- read.delim(file=ampliconsfile, sep='\t', header=T) 

#get number of variant/sample
temp <- paste(mastrdir,'/compar/summary-compar-', mastr,'.tsv',sep='')
vf <- read.delim(temp, sep='\t',header=T, stringsAsFactors=F)
sys_output <- file.remove(temp)

read_cutoff <- 10
cov_cutoff <- 20
```



# `r mastr[1]` 
## `r Sys.Date()`
<br><br>

## Sample statistics
#### per sample statistics: # of reads per sample, fraction of target region covered > 20x per sample and # of variants per sample
<br><br>

```{r prepare_samples_data, echo=FALSE, message=FALSE, results='asis', warning=FALSE}
rf <- demultiplex%>%filter(!grepl('blanco',tolower(SampleID)))%>%
    mutate(sample=SampleID, reads=NumberOfClustersPF)%>%
    select(sample,reads)

vf <- vf%>%filter(!grepl('blanco|sam-crsbwa',tolower(sample)))%>%
  mutate(sample = sub('gatk-crsbwa-','',sample))%>%
  mutate(variants=v.count)%>%select(sample,variants)

if (nrow(frac_cov)) {
	frac_cov$region_size<-sum(frac_cov%>%mutate(size=end-begin)%>%select(size))
	cf <- frac_cov%>%gather(sample,frac,-name,-chr,-begin,-end,-region_size)%>%filter(!grepl('blanco',tolower(sample)))%>%
	    mutate(weighted_frac=((end-begin)/region_size)*frac)%>%select(sample, weighted_frac)%>%
	    group_by(sample)%>%summarize(frac=sum(weighted_frac))
	
	df <- left_join(left_join(rf,vf),cf)  
	data = T
} else {
	data = F
}

```

```{r plot_samples, echo=FALSE, message=FALSE, results='asis', warning=FALSE}
bucketsize <-as.character(signif((max(rf$reads) - min(rf$reads))/10, 1))

plot(google_jsapi_local(gvisHistogram(rf%>%select(sample,reads),
    options=list(title="Histogram of number of reads per sample",legend="none",
    histogram=paste("{bucketSize:", bucketsize,"}", sep=" "), gvis.editor="Edit")), local_jsapi))
if (data) {
plot(google_jsapi_local(gvisHistogram(cf%>%select(sample,frac),
    options=list(title=paste("Histogram of fraction of target region covered above ", frac,"x per sample", sep=""),
    legend="none", histogram="{bucketSize:0.1}", gvis.editor="Edit")), local_jsapi))
}

plot(google_jsapi_local(gvisHistogram(vf%>%select(sample,variants),
    options=list(title="Histogram of number of variants per sample",legend="none", gvis.editor="Edit")), local_jsapi))
```
<br><br>
```{r table_samples, echo=FALSE, message=FALSE, results='asis', warning=FALSE}
if (data) {
datatable(df%>%mutate(`fraction of target region covered > 20x` = round(frac,2), comments=ifelse(reads<read_cutoff,"not analyzed",""))%>%select(-frac), filter = 'top')
}
```
<br><br>

## Skipped samples  
#### these samples are not analyzed due to the low number of reads
<br><br>

```{r get_skipped_samples, echo=FALSE, message=FALSE, results='asis'}
  skipped<-rf%>%filter(reads<read_cutoff)%>%select(sample,reads)
```
`r if (nrow(skipped)==0) {'No samples skipped'}`
```{r skipped_samples_table, echo=FALSE, message=FALSE, results='asis'}
  if (nrow(skipped)>0) {datatable(skipped, filter = 'top')}
```

<br><br><br><br>

## Amplicon statistics
#### per amplicon coverage statistics averaged over all samples within experiment (excluding blancos)
<br><br>

```{r prepare_amplicons_data, echo=FALSE, message=FALSE, results='asis'}
ac <- avg_cov%>%gather(sample,coverage,-name,-chr,-begin,-end)%>%
    filter(!grepl('blanco',tolower(sample)))%>%group_by(name)%>%
    summarize(average_coverage=mean(coverage))
if (data) {
fc <- frac_cov%>%gather(sample,coverage,-name,-chr,-begin,-end, -region_size)%>%
    filter(!grepl('blanco',tolower(sample)))%>%group_by(name)%>%
    summarize(frac=mean(coverage))
afc <- left_join(ac,fc)
}

```


#### Design: `r strsplit(mastr, '_')[[1]][4]` - `r nrow(amplicons)` amplicons 
<br>
```{r table_design, echo=FALSE, message=FALSE, results='asis'}
datatable(amplicons, filter = 'top')	
```
<br>
```{r plot_amplicons, echo=FALSE, message=FALSE, results='asis'}

if (data) {
bucketsize <-as.character(signif((max(afc$average_coverage) - min(afc$average_coverage))/10, 1))

plot(google_jsapi_local(gvisHistogram(afc%>%select(name,average_coverage),
    options=list(title="Histogram of average coverage per amplicon",
    #hAxis="{title:'Average coverage of amplicon'}", vAxis="{title:'Frequency'}", 
    legend="none",
    histogram=paste("{bucketSize:", bucketsize,"}", sep=" "), gvis.editor="Edit")), local_jsapi))

plot(google_jsapi_local(gvisHistogram(afc%>%select(name,frac), 
    options=list(title=paste("Histogram of fraction covered above ", frac, "x per amplicon", sep=""),
    #hAxis="{title:'Fraction of amplicon covered >20x'}", vAxis="{title:'Frequency'}",
    legend="none", histogram="{bucketSize:0.1}", gvis.editor="Edit")), local_jsapi))
}
```
<br><br>
```{r table_amplicon_coverage, echo=FALSE, message=FALSE, results='asis'}
if (data) {
datatable(afc%>%mutate(`average coverage` = round(average_coverage, 2), `fraction above 20x` = round(frac,2))%>%select(-average_coverage, -frac) , filter = 'top')
}
```
<br><br><br><br>

